```{r, include=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
source("simulateSeason.R")

p_week <- 2
p_run <- 500


p_teams_stephen <- read.csv("teams_stephen.csv")
```

---
title: `r paste("Stephen's RLCS Season 7 Fantasy League", '<br>', 'Week', p_week, "Report")`
output: html_notebook
---
Date published: April 16, 2019
<br><br>

Selected teams:<br>
```{r, include=FALSE}
## Run optimizer to find a team for this week.
stephen_lastTeam <- c(which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[1,(p_week)])), 
                      which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[2,(p_week)])), 
                      which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[3,(p_week)])), 
                      which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[4,(p_week)])),
                      which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[5,(p_week)])), 
                      which(weeklyPlayerData[[p_week - 1]]$Player == as.character(p_teams_stephen[6,(p_week)]))) 
stephen_newTeam <- selectTeam(stephen_lastTeam, weeklyPlayerData[[p_week - 1]], p_run)
```

```{r, echo=FALSE}
## Prep new table showing old teams + optimized team for this week.
subset(p_teams_stephen, select = c(1, rep(2:(p_week + 1))))

kable(subset(p_teams_stephen, select = c(1, rep(2:(p_week + 1)))), caption="Stephen's Weekly Teams") %>% kable_styling
```
<br>

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
